---
title: "Medical Student Attitudes Toward Personalized Medicine Report"
author: "Kipp Johnson"
date: "May 15, 2015"
output: html_document
---

## Introduction

This analysis is conducted in R using R Markdown with Knitr for report generation. The raw data as well as the source code for every table, figure, and calculation is accessible at https://www.github.com/kippjohnson/PMQ/ 

Much of the actual analysis code is omitted from being embedded in the printout of this report because it's tedious to look at along with the results. However, it is completely available in the markdown file in the Github repository (ProjectReport.Rmd).

NOTE: I got tired of typing "after correction for multiple testing" report. All P-Values which are reported as significant in this text have undergone correction for multiple testing using either the Bonferroni, Tukey honest significant differences method, or Benjami-Hochberg method. I usually use the Bonferroni method (0.05/n tests); in one section it makes more sense to use a more elaborate method (B-H) or Tukey, and it is stated when it is used. Tukey HSD is used following significant ANOVA results.

If you are trying to replicate this report, ensure the following R packages are installed and loaded:
```{r Call required libraries, error=FALSE,warning=FALSE,autodep=FALSE,collapse=TRUE,message=FALSE}
library(knitr) # For report generation, not strictly necessary to run code
library(psych)
library(dunn.test)
```

R code for reading in the data from the Github Repository (/kippjohnson/PMQ):
```{r Read in data from Github, results='hide'}
rm(list=ls())
tmp <- tempfile()
download.file("https://raw.githubusercontent.com/kippjohnson/PMQ/master/SurveyResponses.csv", destfile=tmp, method="curl")
infile <- read.csv(tmp,header=TRUE)
```

## Survey Demographics Table
```{r Demographics Table, echo=FALSE}
nMales = table(infile$Q27)[[1]]
nFemales = table(infile$Q27)[[2]]
nNoSex = table(infile$Q27,exclude=NULL)[[3]]

nMS1 = table(infile$Q28.2)[[1]]
nMS2 = table(infile$Q28.2)[[2]]
nMS3 = table(infile$Q28.2)[[3]]
nMS4 = table(infile$Q28.2)[[4]]
nMSNone = table(infile$Q28.2,exclude=NULL)[[5]]

nDual = table(infile$Q29.1)[[1]]
nResearch = table(infile$Q30.1)[[1]]

demog <-  data.frame(c(nMales,nFemales,nNoSex,nMS1,nMS2,nMS3,nMS4,nMSNone,nDual,nResearch))
colnames(demog) <- "Number of Students"
row.names(demog) <- c("Male","Female","No Sex Given","MS1","MS2","MS3","MS4","No Year Given","Total with Research Interest","Total Dual Degree")

demog <- mutate(demog, PercentTotal = demog[,1] / 212)

kable(demog, digits=2,padding=0)
```


### EBPAS Statistics
The first step is to compute EBPAS total score, along with its subsets for scores of openness, and divergence. Education is not included in the EBPAS. Questions 1-12 excluding 3, 6, 9, and 11 define the EBPAS scale on the survey. 3, 6, 9, and 11 are the education questions. There are a number of people who did not completely fill out the first 12 questions of the survey, and for the analysis they will be dropped because we have a large enough number of respondents without them.

Questions 2, 4, 5, and 8 are 'divergence' questions, where the questions have answers which have been formulated to be the inverse of the answering scale. They have been reversed in our analysis.

```{r Drop observations that are incomplete in EBPAS}
infile2 <- mutate(infile, total1to12 = Q1+Q2+Q3+Q4+Q5+Q6+Q7+Q8+Q9+Q10+Q11+Q12)
infile3 <- infile2[-which(is.na(infile2$total1to12)),] #drop incompletes
```

Number of people who did not completely fill out the first 12 questions on the survey: **`r length(which(is.na(infile2$total1to12)))`**

Questions here:  Do you agree with my decision to drop  **`r length(which(is.na(infile2$total1to12)))`** individuals from the rest of the study? I think it was the best way to proceed, because we have a large number of responses without them and it makes everything harder and less reliable if we choose to proceed with a large amount of missing data.

```{r Making EBPAS openness divergence education columns, echo=FALSE}
infile3 <- mutate(infile3, EBPAS = Q1+Q2+Q4+Q5+Q7+Q8+Q10+Q12)
infile3 <- mutate(infile3, openness = Q1+Q7+Q10+Q12)
infile3 <- mutate(infile3, divergence = Q2+Q4+Q5+Q8)
infile3 <- mutate(infile3, education = Q3+Q6+Q9+Q11)
```

#### __Initial__ Cronbach's Alpha Calculations
For Cronbach's alpha, we use the alpha() function from the psych package in R. The EBPAS cronbach's alpha is taken from the literature {0.78} (Overby et al., J Pers. Med. 2014), as was done in the paper from which we are modeling this.

```{r Define Summation function, echo=FALSE}
sums <- function(somevector){
  n <- length(somevector)
  xbar <- mean(somevector)
  s <- sd(somevector)
  mn <- min(somevector)
  mx <- max(somevector)
  ran <- mx - mn

  return(c(n, xbar, s, mn, mx, ran))
}
```


```{r Getting Initialized, echo=FALSE, warning=FALSE}
### Compute statistics for later table

EBPASstats <- sums(infile3$EBPAS)
opennessstats <- sums(infile3$openness)
divergencestats <- sums(infile3$divergence)
educationstats <- sums(infile3$education)


divergence_corrected <- abs(infile3[,c("Q2","Q4","Q5","Q8")] - 6)
#EBPAS_alpha <- alpha(infile3[,c(2,4,7,8,10,11,12,13,div_corrected)])

EBPAS_alpha <- 0.78
#EBPAS_alpha <- alpha(infile3[,c("Q1","Q2","Q4","Q5","Q7","Q8","Q10","Q12")])
openness_alpha <- alpha(infile3[,c("Q1","Q7","Q10","Q12")])
#divergence_alpha <- alpha(infile3[,c("Q2","Q4","Q5","Q8")])
divergence_alpha <- alpha(divergence_corrected)
education_alpha <- alpha(infile3[,c("Q3","Q6","Q9","Q11")]) 

EBPASstats <- c(EBPASstats, EBPAS_alpha)
#EBPASstats <- c(EBPASstats, EBPAS_alpha$total[[1]])
opennessstats <- c(opennessstats, openness_alpha$total[[1]])
divergencestats <- c(divergencestats, divergence_alpha$total[[1]])
educationstats <- c(educationstats, education_alpha$total[[1]])

EBPAStable <- t(data.frame(EBPASstats,educationstats, divergencestats, opennessstats))
colnames(EBPAStable)  <- c("N","Mean","SD","Min","Max","Range","Alpha")
rownames(EBPAStable) <- c("EBPAS", "education", "divergence","openness")
```

`r kable(EBPAStable, digits=3)`

#### Cronbach's alpha for different possible 3-question subsets of education
From the education questions 3, 6, 9, and 11, we can make four different possible subsets of three questions: 3, 6, 9; 3, 9, 11; 3, 6, 11; 6, 9, 11. Here, we compute the Cronbach's alpha for these possible subsets of questions.

```{r, echo=FALSE, warning=FALSE}
subset369  <- alpha(infile3[,c("Q3","Q6","Q9")])$total[[1]]
subset3911 <- alpha(infile3[,c("Q3","Q9","Q11")])$total[[1]]
subset3611 <- alpha(infile3[,c("Q3","Q6","Q11")])$total[[1]]
subset6911 <- alpha(infile3[,c("Q6","Q9","Q11")])$total[[1]]

subsettable <- t(data.frame(subset369, subset3911, subset3611, subset6911))
colnames(subsettable) <- c("Alpha")
rownames(subsettable) <- c("Questions 3, 9, 9","Questions 3, 9, 11", "Questions 3, 6, 11", "Questions 6, 9, 11")
kable(subsettable)
```

As you can see, none of these are above 0.70, although the grouping of questions 3, 6, and 11 is close. Apparently question number 9 elicited different responses from the other three educational questions. We we do later find a different association for number 9 with our covariates than we do for questions 3, 6, and 11. 

### Computing Cronbach's alpha for questions 18-21, 22-25, and 18-25 combined.

Questions 18-21 ask the subject "How comfortable are you in your knowledge about [various genomic testing concepts]." Questions 22-25 ask the subject "How comfortable are you in your ability to [apply various genomic testing concepts in a clinical setting]". We can also combine all 8 questions together as a general genomic familiarity category. To see if these sections assessed the same central ability, we can compute Cronbach's alpha for each of them:

```{r Calculation of Genomics Cronbach Alphas, echo=FALSE}

knowledge_alpha <- alpha(infile3[,c("Q18","Q19","Q20","Q21")])
ability_alpha <-   alpha(infile3[,c("Q22","Q23","Q24","Q25")])
knowledge_ability_alpha <-   alpha(infile3[,c("Q18","Q19","Q20","Q21","Q22","Q23","Q24","Q25")])

outka <- data.frame(knowledge_alpha$total[[1]], ability_alpha$total[[1]], knowledge_ability_alpha$total[[1]])
colnames(outka) <- c("Questions 18-21 Alpha", "Questions 22-25 Alpha", "Questions 18-25 (Combined) Alpha")
kable(outka)
```

As you can see, the Cronbach's alpha for these sections are extremely high.

## Data Analysis & Significance Tests

#### Step 1: Frequencies

*Question Response Frequencies*: Tables of each question's (1-25) response frequency. These questions are categorized as:

* EBPAS & education questions (1-12)
* Attitudes toward DTC (13-15)
* Comfort using technology (16, 17)
* Knowledge of genomic testing concepts (18-21)
* Ability to understand genomic testing concepts (22-25)

The coding for the question responses is given in the file "DataCoding.txt" in the Github repository. Most of the time it's obvious. 

```{r, echo=FALSE}
kable(data.frame(table(infile$Q1)),col.names=c("Question 1", "Frequency"),align="l")
kable(data.frame(table(infile$Q2)),col.names=c("Question 2", "Frequency"),align="l")
kable(data.frame(table(infile$Q3)),col.names=c("Question 3", "Frequency"),align="l")
kable(data.frame(table(infile$Q4)),col.names=c("Question 4", "Frequency"),align="l")
kable(data.frame(table(infile$Q5)),col.names=c("Question 5", "Frequency"),align="l")
kable(data.frame(table(infile$Q6)),col.names=c("Question 6", "Frequency"),align="l")
kable(data.frame(table(infile$Q7)),col.names=c("Question 7", "Frequency"),align="l")
kable(data.frame(table(infile$Q8)),col.names=c("Question 8", "Frequency"),align="l")
kable(data.frame(table(infile$Q9)),col.names=c("Question 9", "Frequency"),align="l")
kable(data.frame(table(infile$Q10)),col.names=c("Question 10", "Frequency"),align="l")
kable(data.frame(table(infile$Q11)),col.names=c("Question 11", "Frequency"),align="l")
kable(data.frame(table(infile$Q12)),col.names=c("Question 12", "Frequency"),align="l")

kable(data.frame(table(infile$Q13)),col.names=c("Question 13", "Frequency"),align="l") # Have heard of DTC: 50 no, 101 yes
kable(data.frame(table(infile$Q14)),col.names=c("Question 14", "Frequency"),align="l") # Would use DTC: 73 would not use, 121 would use, 9 did use
kable(data.frame(table(infile$Q15)),col.names=c("Question 15", "Frequency"),align="l") # Can interpret DTC: 35 str. disagree, 30 dis, 72 uncertain, 58 agree, 14 str. agree
kable(data.frame(table(infile$Q16)),col.names=c("Question 16", "Frequency"),align="l") # Vast majority comfortable with computers
kable(data.frame(table(infile$Q17)),col.names=c("Question 17", "Frequency"),align="l") # Comfort with using EPIC

kable(data.frame(table(infile$Q18)),col.names=c("Question 18", "Frequency"),align="l") # Comfort with basic genomic testing concepts and terminology
kable(data.frame(table(infile$Q19)),col.names=c("Question 19", "Frequency"),align="l") # Comfort with pharmacogenomics knowledge
kable(data.frame(table(infile$Q20)),col.names=c("Question 20", "Frequency"),align="l") # Comfort with knowledge about genetic variation
kable(data.frame(table(infile$Q21)),col.names=c("Question 21", "Frequency"),align="l") # Comfort with knolwedge about NGS

kable(data.frame(table(infile$Q22)),col.names=c("Question 22", "Frequency"),align="l") # Ability to recommend genetic testing
kable(data.frame(table(infile$Q23)),col.names=c("Question 23", "Frequency"),align="l") # Ability to understand genomic test results
kable(data.frame(table(infile$Q24)),col.names=c("Question 24", "Frequency"),align="l") # Ability to explain genomic test results to patients
kable(data.frame(table(infile$Q25)),col.names=c("Question 25", "Frequency"),align="l") # Ability to make treatment recommendations based upon genomic test results
```

### Step 2: EBPAS Collapsed T-Tests

First, answers for questions 13-25 were tested for an association with EBPAS Score (Questions 1-12 excluding the education questions) using ANOVA followed by Tukey Honest Signficant Differences. Second, the answers were collapsed into binary categories and T-tests for association with EBPAS score were performed.

The R output for each ANOVA and Collapsed T-test is shown below. After the end of the output there is a table summarizing the results in a fashion analagous to Table 6 in Overby et al.

The format for each ANOVA is EBPAS ~ Question Answer Choices. After that, if the ANOVA is significant, a Tukey HSD test is computed. The TukeyHSD test shows which answer choices in the ANOVA results are actually associated with significantly different EBPAS scores.

The collapsed T-tests were collapsed by assigning the responses in the first three Likert Groups to one group (For example, "Not At All Comfortable, Not Very Comfortable, and Neither Comfortable nor Uncomfortable" were collapsed to *Group 1*), and collapsing the remaining Likery Groups to a second group ("Comfortable and Very Comfortable were assigned to *Group Two*") 

Note: The EBPAS scores totals are approximately normal by visual analysis:

```{r EBPASPLOT, echo=FALSE}
hist(infile3$EBPAS, xlab="EBPAS Score", main="Histogram of EBPAS Totals")
```

##### Question 13
```{r Q13, echo=FALSE, results='hold', fig.show='hide'}
### Q13
#Q13 T-test
t.test(infile3$EBPAS ~ infile3$Q13) #NS
boxplot(EBPAS ~ Q13, data=infile3)
```

##### Question 14
```{r Q14, echo=FALSE, results='hold', fig.show='hide'}
### Q14
#Q14 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q14))) #NS
  TukeyHSD(aov(infile3$EBPAS~ as.factor(infile3$Q14)))
  boxplot(EBPAS ~ Q14, data=infile3)

#Q14 Collapsed t-test
infile3$Q14c <- infile3$Q14
infile3$Q14c[infile3$Q14c==3] <- 2
t.test(infile3$EBPAS ~ infile3$Q14c) # Significant
CT14 <- t.test(infile3$EBPAS ~ infile3$Q14c) # Significant)

s14 <- ddply(infile3, ~infile3$Q14c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))
```

##### Question 15
```{r Q15, echo=FALSE, results='hold', fig.show='hide'}

### Q15
# Q15 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q15))) #significant
  TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q15)))
  boxplot(EBPAS ~ Q15, data=infile3)

#Q15 Collapsed t-test
infile3$Q15c <- infile3$Q15
infile3$Q15c[infile3$Q15c==2] <- 1
infile3$Q15c[infile3$Q15c==3] <- 1
#infile3$Q15c[infile3$Q15c==3] <- 2
infile3$Q15c[infile3$Q15c==4] <- 2
infile3$Q15c[infile3$Q15c==5] <- 2

table(infile3$Q15)
table(infile3$Q15c)
t.test(infile3$EBPAS ~ infile3$Q15c) #Significant Note: depends upon assignment of category 3
CT15 <- t.test(infile3$EBPAS ~ infile3$Q15c) # Significant)

s15 <- ddply(infile3, ~infile3$Q15c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 16
```{r Q16, echo=FALSE, results='hold', fig.show='hide'}
### Q16
#Q16 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q16))) #significant
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q16)))
boxplot(EBPAS ~ Q16, data=infile3)

#Q16 Collapsed t-test
infile3$Q16c <- infile3$Q16
infile3$Q16c[infile3$Q16c==2] <- 1
infile3$Q16c[infile3$Q16c==3] <- 1
infile3$Q16c[infile3$Q16c==4] <- 2
infile3$Q16c[infile3$Q16c==5] <- 2

table(infile3$Q16)
table(infile3$Q16c)
t.test(infile3$EBPAS ~ infile3$Q16c) # NS
CT16 <- t.test(infile3$EBPAS ~ infile3$Q16c) # Significant)
s16 <- ddply(infile3, ~infile3$Q16c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 17
```{r Q17, echo=FALSE, results='hold', fig.show='hide'}

### Q17
#Q17 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q17)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q17)))
boxplot(EBPAS ~ Q17, data=infile3)

#Q17 Collapsed t-test
infile3$Q17c <- infile3$Q17
infile3$Q17c[infile3$Q17c==2] <- 1
infile3$Q17c[infile3$Q17c==3] <- 1
infile3$Q17c[infile3$Q17c==4] <- 2
infile3$Q17c[infile3$Q17c==5] <- 2

table(infile3$Q17)
table(infile3$Q17c)
t.test(infile3$EBPAS ~ infile3$Q17c) # NS
CT17 <- t.test(infile3$EBPAS ~ infile3$Q17c) # Significant)
s17 <- ddply(infile3, ~infile3$Q17c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 18
```{r Q18, echo=FALSE, results='hold', fig.show='hide'}
### Q18
#Q18 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q18)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q18)))
boxplot(EBPAS ~ Q18, data=infile3)

#Q18 Collapsed t-test
infile3$Q18c <- infile3$Q18
table(infile3$Q18)

infile3$Q18c[infile3$Q18c==2] <- 1
infile3$Q18c[infile3$Q18c==3] <- 1
infile3$Q18c[infile3$Q18c==4] <- 2
infile3$Q18c[infile3$Q18c==5] <- 2

table(infile3$Q18c)
t.test(infile3$EBPAS ~ infile3$Q18c) # Significant
CT18 <- t.test(infile3$EBPAS ~ infile3$Q18c) # Significant)
s18 <- ddply(infile3, ~infile3$Q18c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 19
```{r Q19, echo=FALSE, results='hold', fig.show='hide'}
### Q19
#Q19 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q19)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q19)))
boxplot(EBPAS ~ Q19, data=infile3)

#Q19 Collapsed t-test
infile3$Q19c <- infile3$Q19
table(infile3$Q19)

infile3$Q19c[infile3$Q19c==2] <- 1
infile3$Q19c[infile3$Q19c==3] <- 1
infile3$Q19c[infile3$Q19c==4] <- 2
infile3$Q19c[infile3$Q19c==5] <- 2

table(infile3$Q19c)
t.test(infile3$EBPAS ~ infile3$Q19c) # Significant
CT19 <- t.test(infile3$EBPAS ~ infile3$Q19c) # Significant)
s19 <- ddply(infile3, ~infile3$Q19c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 20
```{r Q20, echo=FALSE, results='hold', fig.show='hide'}

### Q20
#Q20 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q20)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q20)))
boxplot(EBPAS ~ Q20, data=infile3)

#Q20 Collapsed t-test
infile3$Q20c <- infile3$Q20
table(infile3$Q20)

infile3$Q20c[infile3$Q20c==2] <- 1
infile3$Q20c[infile3$Q20c==3] <- 1
infile3$Q20c[infile3$Q20c==4] <- 2
infile3$Q20c[infile3$Q20c==5] <- 2

table(infile3$Q20c)
t.test(infile3$EBPAS ~ infile3$Q20c) # Significant
CT20 <- t.test(infile3$EBPAS ~ infile3$Q20c) # Significant)
s20 <- ddply(infile3, ~infile3$Q20c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 21
```{r Q21, echo=FALSE, results='hold', fig.show='hide'}

### Q21
#Q21 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q21)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q21)))
boxplot(EBPAS ~ Q21, data=infile3)

#Q21 Collapsed t-test
infile3$Q21c <- infile3$Q21
table(infile3$Q21)

infile3$Q21c[infile3$Q21c==2] <- 1
infile3$Q21c[infile3$Q21c==3] <- 1
infile3$Q21c[infile3$Q21c==4] <- 2
infile3$Q21c[infile3$Q21c==5] <- 2

table(infile3$Q21c)
t.test(infile3$EBPAS ~ infile3$Q21c) # Significant)
CT21 <- t.test(infile3$EBPAS ~ infile3$Q21c) # Significant)
s21 <- ddply(infile3, ~infile3$Q21c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 22
```{r Q22, echo=FALSE, results='hold', fig.show='hide'}
### Q22
#Q22 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q22)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q22)))
boxplot(EBPAS ~ Q22, data=infile3)

#Q22 Collapsed t-test
infile3$Q22c <- infile3$Q22
table(infile3$Q22)

infile3$Q22c[infile3$Q22c==2] <- 1
infile3$Q22c[infile3$Q22c==3] <- 1
infile3$Q22c[infile3$Q22c==4] <- 2
infile3$Q22c[infile3$Q22c==5] <- 2

table(infile3$Q22c)
t.test(infile3$EBPAS ~ infile3$Q22c) # Significant)
CT22 <- t.test(infile3$EBPAS ~ infile3$Q22c) # Significant)
s22 <- ddply(infile3, ~infile3$Q22c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 23
```{r Q23, echo=FALSE, results='hold', fig.show='hide'}

### Q23
#Q23 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q23)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q23)))
boxplot(EBPAS ~ Q23, data=infile3)

#Q23 Collapsed t-test
infile3$Q23c <- infile3$Q23
table(infile3$Q23)

infile3$Q23c[infile3$Q23c==2] <- 1
infile3$Q23c[infile3$Q23c==3] <- 1
infile3$Q23c[infile3$Q23c==4] <- 2
infile3$Q23c[infile3$Q23c==5] <- 2

table(infile3$Q23c)
t.test(infile3$EBPAS ~ infile3$Q23c) # Significant)
CT23 <- t.test(infile3$EBPAS ~ infile3$Q23c) # Significant)
s23 <- ddply(infile3, ~infile3$Q23c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```

##### Question 24
```{r Q24, echo=FALSE, results='hold', fig.show='hide'}

### Q24
#Q24 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q24)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q24)))
boxplot(EBPAS ~ Q24, data=infile3)

#Q24 Collapsed t-test
infile3$Q24c <- infile3$Q24
table(infile3$Q24)

infile3$Q24c[infile3$Q24c==2] <- 1
infile3$Q24c[infile3$Q24c==3] <- 1
infile3$Q24c[infile3$Q24c==4] <- 2
infile3$Q24c[infile3$Q24c==5] <- 2

table(infile3$Q24c)
t.test(infile3$EBPAS ~ infile3$Q24c) # Significant)
CT24 <- t.test(infile3$EBPAS ~ infile3$Q24c) # Significant)
s24 <- ddply(infile3, ~infile3$Q24c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))
```

##### Question 25
```{r Q25, echo=FALSE, results='hold', fig.show='hide'}

### Q25
#Q25 ANOVA
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q25)))
TukeyHSD(aov(infile3$EBPAS ~ as.factor(infile3$Q25)))
boxplot(EBPAS ~ Q25, data=infile3)

#Q25 Collapsed t-test
infile3$Q25c <- infile3$Q25
table(infile3$Q25)

infile3$Q25c[infile3$Q25c==2] <- 1
infile3$Q25c[infile3$Q25c==3] <- 1
infile3$Q25c[infile3$Q25c==4] <- 2
infile3$Q25c[infile3$Q25c==5] <- 2

table(infile3$Q25c)
t.test(infile3$EBPAS ~ infile3$Q25c) # Significant)
CT25 <- t.test(infile3$EBPAS ~ infile3$Q25c) # Significant)
s25 <- ddply(infile3, ~infile3$Q25c, summarize, N=length(EBPAS), mean=mean(EBPAS), SD=sd(EBPAS))

```


We are doing 12 different significance tests (13-25). To correct for multiple testing, we can use the Bonferroni correction of alpha/number of tests, giving us P=`r 0.05/12`

#### Summary Table of Results from Collapsed T-tests (Analagous to Table. 6, Overby et al.)
```{r Summary table of Collapsed T Test Results (EBPAS), echo=FALSE}

Pcritical <- 0.05/12

print(c("Critical P-Value:  ", Pcritical) )


ebpas_14adj <- CT14$p.value < Pcritical
ebpas_15adj <- CT15$p.value < Pcritical
ebpas_16adj <- CT16$p.value < Pcritical
ebpas_17adj <- CT17$p.value < Pcritical
ebpas_18adj <- CT18$p.value < Pcritical
ebpas_19adj <- CT19$p.value < Pcritical
ebpas_20adj <- CT20$p.value < Pcritical
ebpas_21adj <- CT21$p.value < Pcritical
ebpas_22adj <- CT22$p.value < Pcritical
ebpas_23adj <- CT23$p.value < Pcritical
ebpas_24adj <- CT24$p.value < Pcritical
ebpas_25adj <- CT25$p.value < Pcritical

q14.1 <- c(s14$N[1], s14$mean[1], s14$SD[1], CT14$p.value, ebpas_14adj)
q14.2 <- c(s14$N[2], s14$mean[2], s14$SD[2], CT14$p.value, ebpas_14adj)
q15.1 <- c(s15$N[1], s15$mean[1], s15$SD[1], CT15$p.value, ebpas_15adj)
q15.2 <- c(s15$N[2], s15$mean[2], s15$SD[2], CT15$p.value, ebpas_15adj)
q16.1 <- c(s16$N[1], s16$mean[1], s16$SD[1], CT16$p.value, ebpas_16adj)
q16.2 <- c(s16$N[2], s16$mean[2], s16$SD[2], CT16$p.value, ebpas_16adj)
q17.1 <- c(s17$N[1], s17$mean[1], s17$SD[1], CT17$p.value, ebpas_17adj)
q17.2 <- c(s17$N[2], s17$mean[2], s17$SD[2], CT17$p.value, ebpas_17adj)
q18.1 <- c(s18$N[1], s18$mean[1], s18$SD[1], CT18$p.value, ebpas_18adj)
q18.2 <- c(s18$N[2], s18$mean[2], s18$SD[2], CT18$p.value, ebpas_18adj)
q19.1 <- c(s19$N[1], s19$mean[1], s19$SD[1], CT19$p.value, ebpas_19adj)
q19.2 <- c(s19$N[2], s19$mean[2], s19$SD[2], CT19$p.value, ebpas_19adj)
q20.1 <- c(s20$N[1], s20$mean[1], s20$SD[1], CT20$p.value, ebpas_20adj)
q20.2 <- c(s20$N[2], s20$mean[2], s20$SD[2], CT20$p.value, ebpas_20adj)
q21.1 <- c(s21$N[1], s21$mean[1], s21$SD[1], CT21$p.value, ebpas_21adj)
q21.2 <- c(s21$N[2], s21$mean[2], s21$SD[2], CT21$p.value, ebpas_21adj)
q22.1 <- c(s22$N[1], s22$mean[1], s22$SD[1], CT22$p.value, ebpas_22adj)
q22.2 <- c(s22$N[2], s22$mean[2], s22$SD[2], CT22$p.value, ebpas_22adj)
q23.1 <- c(s23$N[1], s23$mean[1], s23$SD[1], CT23$p.value, ebpas_23adj)
q23.2 <- c(s23$N[2], s23$mean[2], s23$SD[2], CT23$p.value, ebpas_23adj)
q24.1 <- c(s24$N[1], s24$mean[1], s24$SD[1], CT24$p.value, ebpas_24adj)
q24.2 <- c(s24$N[2], s24$mean[2], s24$SD[2], CT24$p.value, ebpas_24adj)
q25.1 <- c(s25$N[1], s25$mean[1], s25$SD[1], CT25$p.value, ebpas_25adj)
q25.2 <- c(s25$N[2], s25$mean[2], s25$SD[2], CT25$p.value, ebpas_25adj)

out <- data.frame(t(data.frame(q14.1,q14.2,
                               q15.1,q15.2,
                               q16.1,q16.2,
                               q17.1,q17.2,
                               q18.1,q18.2,
                               q19.1,q19.2,
                               q20.1,q20.2,
                               q21.1,q21.2,
                               q22.1,q22.2,
                               q23.1,q23.2,
                               q24.1,q24.2,
                               q25.1,q25.2)))

colnames(out) <- c("N","Mean","SD","T-Test P-Value","P-Value Significant? (1=Yes, 0=No)")
row.names(out) <- c("Question 14 Group 1",
                    "Question 14 Group 2",
                    "Question 15 Group 1",
                    "Question 15 Group 2",
                    "Question 16 Group 1",
                    "Question 16 Group 2",
                    "Question 17 Group 1",
                    "Question 17 Group 2",
                    "Question 18 Group 1",
                    "Question 18 Group 2",
                    "Question 19 Group 1",
                    "Question 19 Group 2",
                    "Question 20 Group 1",
                    "Question 20 Group 2",
                    "Question 21 Group 1",
                    "Question 21 Group 2",
                    "Question 22 Group 1",
                    "Question 22 Group 2",
                    "Question 23 Group 1",
                    "Question 23 Group 2",
                    "Question 24 Group 1",
                    "Question 24 Group 2",
                    "Question 25 Group 1",
                    "Question 25 Group 2")

kable(out, digits=3)           
        
```

```{r, echo=FALSE}
ddply(infile3, ~Q19c, summarize, n=length(EBPAS), mean=mean(EBPAS))
ddply(infile3, ~Q22c, summarize, n=length(EBPAS), mean=mean(EBPAS))
ddply(infile3, ~Q25c, summarize, n=length(EBPAS), mean=mean(EBPAS))
```
After correction for multiple testing, EBPAS is significantly associated with questions 19, 22, and 25.

* On question 19, those who answered "not at all/not very/neither comfortable not uncomfortable" had a significantly lower EBPAS score than those who answered "comfortable or very comfortable" (P=<0.0001)
* On question 22, those who answered "not at all/not very/neither comfortable not uncomfortable" had a significantly lower EBPAS score than those who answered "comfortable or very comfortable" (P=<0.0004)
* On question 23, those who answered "not at all/not very/neither comfortable not uncomfortable" had a significantly lower EBPAS score than those who answered "comfortable or very comfortable" (P=<0.0004)

### Statistical Tests (ANOVA and Collapsed T-tests) for four education questions

In the previous section, we performed ANOVA and collapsed T tests for the 8 EBPAS questions on the predictor questions 13-25. For the education questions 3, 6, 9, and 11, we cannot combine them into one category because Cronbach's alpha is <0.7 for them. However, we can analyze the questions individually, as is done here:

##### T-Tests for association with Education question 3
```{r Q3 on Education, echo=FALSE, results='hold', fig.show='hide'}

### Q3

#Q3 Collapsed t-tests
ed_3on13 <- t.test(infile3$Q3 ~ infile3$Q13)
ed_3on14 <- t.test(infile3$Q3 ~ infile3$Q14c)
ed_3on15 <- t.test(infile3$Q3 ~ infile3$Q15c)
ed_3on16 <- t.test(infile3$Q3 ~ infile3$Q16c)
ed_3on17 <- t.test(infile3$Q3 ~ infile3$Q17c)
ed_3on18 <- t.test(infile3$Q3 ~ infile3$Q18c)
ed_3on19 <- t.test(infile3$Q3 ~ infile3$Q19c)
ed_3on20 <- t.test(infile3$Q3 ~ infile3$Q20c)
ed_3on21 <- t.test(infile3$Q3 ~ infile3$Q21c)
ed_3on22 <- t.test(infile3$Q3 ~ infile3$Q22c)
ed_3on23 <- t.test(infile3$Q3 ~ infile3$Q23c)
ed_3on24 <- t.test(infile3$Q3 ~ infile3$Q24c)
ed_3on25 <- t.test(infile3$Q3 ~ infile3$Q25c)

ed_3on13_adj <- ed_3on13$p.value < Pcritical
ed_3on14_adj <- ed_3on14$p.value < Pcritical
ed_3on15_adj <- ed_3on15$p.value < Pcritical
ed_3on16_adj <- ed_3on16$p.value < Pcritical
ed_3on17_adj <- ed_3on17$p.value < Pcritical
ed_3on18_adj <- ed_3on18$p.value < Pcritical
ed_3on19_adj <- ed_3on19$p.value < Pcritical
ed_3on20_adj <- ed_3on20$p.value < Pcritical
ed_3on21_adj <- ed_3on21$p.value < Pcritical
ed_3on22_adj <- ed_3on22$p.value < Pcritical
ed_3on23_adj <- ed_3on23$p.value < Pcritical
ed_3on24_adj <- ed_3on24$p.value < Pcritical
ed_3on25_adj <- ed_3on25$p.value < Pcritical

out3 <- t(data.frame(c(ed_3on13$p.value, ed_3on13_adj),
                   c(ed_3on14$p.value, ed_3on14_adj),
                   c(ed_3on15$p.value, ed_3on15_adj),
                   c(ed_3on16$p.value, ed_3on16_adj),
                   c(ed_3on17$p.value, ed_3on17_adj),
                   c(ed_3on18$p.value, ed_3on18_adj),
                   c(ed_3on19$p.value, ed_3on19_adj),
                   c(ed_3on20$p.value, ed_3on20_adj),
                   c(ed_3on21$p.value, ed_3on21_adj),
                   c(ed_3on22$p.value, ed_3on22_adj),
                   c(ed_3on23$p.value, ed_3on23_adj),
                   c(ed_3on24$p.value, ed_3on24_adj),
                   c(ed_3on25$p.value, ed_3on25_adj)
                   )
                )

colnames(out3) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out3) <- c("Question 13","Question 14","Question 15","Question 16","Question 17","Question 18","Question 19","Question 20","Question 21","Question 22","Question 23","Question 24","Question 25")

kable(out3, digits=6)

ddply(infile3, ~Q15c, summarize, n=length(Q3), mean=mean(Q3))
ddply(infile3, ~Q18c, summarize, n=length(Q3), mean=mean(Q3))
ddply(infile3, ~Q19c, summarize, n=length(Q3), mean=mean(Q3))
ddply(infile3, ~Q23c, summarize, n=length(Q3), mean=mean(Q3))
ddply(infile3, ~Q24c, summarize, n=length(Q3), mean=mean(Q3))
```

* Those who answered question 15 ("I know enough about genomic to undestand DTC") as either strongly/ siagree/disagree/uncertain had a significantly lower agreement with the statement "My medical education has adequately prepared me to practice personalized medicine" than those who answered the question as agree or strongly agree (p=0.000214)
* Those who answered question 18 ("Basic genomic testing concepts and terminology?") as either not at all comfortable/not very comfortable/neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My medical education has adequately prepared me to practice personalized medicine" than those who answered the question" than those who answered the question as comfortable or very comfortable
* Those who answered question 19 ("Pharmacogenomics?") as either not at all comfortable/not very comfortable/neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My medical education has adequately prepared me to practice personalized medicine" than those who answered the question" than those who answered the question as comfortable or very comfortable.
* Those who answered question 23 ("Understand genomic test results?") as either not at all comfortable/not very comfortable/neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My medical education has adequately prepared me to practice personalized medicine" than those who answered the question" than those who answered the question as comfortable or very comfortable.
* Those who answered question 24 ("Explain genomic test results") as either not at all comfortable/not very comfortable/neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My medical education has adequately prepared me to practice personalized medicine" than those who answered the question" than those who answered the question as comfortable or very comfortable.

##### T-Tests for association with Education question 6
```{r Q6 on Education, echo=FALSE, results='hold', fig.show='hide'}
### Q6

#Q6 Collapsed t-tests
ed_6on13 <- t.test(infile3$Q6 ~ infile3$Q13)
ed_6on14 <- t.test(infile3$Q6 ~ infile3$Q14c)
ed_6on15 <- t.test(infile3$Q6 ~ infile3$Q15c)
ed_6on16 <- t.test(infile3$Q6 ~ infile3$Q16c)
ed_6on17 <- t.test(infile3$Q6 ~ infile3$Q17c)
ed_6on18 <- t.test(infile3$Q6 ~ infile3$Q18c)
ed_6on19 <- t.test(infile3$Q6 ~ infile3$Q19c)
ed_6on20 <- t.test(infile3$Q6 ~ infile3$Q20c)
ed_6on21 <- t.test(infile3$Q6 ~ infile3$Q21c)
ed_6on22 <- t.test(infile3$Q6 ~ infile3$Q22c)
ed_6on23 <- t.test(infile3$Q6 ~ infile3$Q23c)
ed_6on24 <- t.test(infile3$Q6 ~ infile3$Q24c)
ed_6on25 <- t.test(infile3$Q6 ~ infile3$Q25c)

ed_6on13_adj <- ed_6on13$p.value < Pcritical
ed_6on14_adj <- ed_6on14$p.value < Pcritical
ed_6on15_adj <- ed_6on15$p.value < Pcritical
ed_6on16_adj <- ed_6on16$p.value < Pcritical
ed_6on17_adj <- ed_6on17$p.value < Pcritical
ed_6on18_adj <- ed_6on18$p.value < Pcritical
ed_6on19_adj <- ed_6on19$p.value < Pcritical
ed_6on20_adj <- ed_6on20$p.value < Pcritical
ed_6on21_adj <- ed_6on21$p.value < Pcritical
ed_6on22_adj <- ed_6on22$p.value < Pcritical
ed_6on23_adj <- ed_6on23$p.value < Pcritical
ed_6on24_adj <- ed_6on24$p.value < Pcritical
ed_6on25_adj <- ed_6on25$p.value < Pcritical

out6 <- t(data.frame(c(ed_6on13$p.value, ed_6on13_adj),
                   c(ed_6on14$p.value, ed_6on14_adj),
                   c(ed_6on15$p.value, ed_6on15_adj),
                   c(ed_6on16$p.value, ed_6on16_adj),
                   c(ed_6on17$p.value, ed_6on17_adj),
                   c(ed_6on18$p.value, ed_6on18_adj),
                   c(ed_6on19$p.value, ed_6on19_adj),
                   c(ed_6on20$p.value, ed_6on20_adj),
                   c(ed_6on21$p.value, ed_6on21_adj),
                   c(ed_6on22$p.value, ed_6on22_adj),
                   c(ed_6on23$p.value, ed_6on23_adj),
                   c(ed_6on24$p.value, ed_6on24_adj),
                   c(ed_6on25$p.value, ed_6on25_adj)
                   )
                )

colnames(out6) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out6) <- c("Question 13","Question 14","Question 15","Question 16","Question 17","Question 18","Question 19","Question 20","Question 21","Question 22","Question 23","Question 24","Question 25")

ddply(infile3, ~Q15c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q18c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q19c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q20c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q21c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q23c, summarize, n=length(Q3), mean=mean(Q6))
ddply(infile3, ~Q24c, summarize, n=length(Q3), mean=mean(Q6))

kable(out6,digits=6)
```

* Those who answered question number 15 ("I know enought about genetics and genomics to understand DTC") as either strongly disagree, disagree, or uncertain had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as agree or strongly agree.
* Those who answered question number 18 ("Basic genomic testing concepts and terminology") as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 19 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 20 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 21 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 23 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 24 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "I know whom to ask questions regarding genomic testing questions" than those who answered the question as comfortable or very comfortable.

##### T-Tests for association with Education question 9
```{r Q9 on Education, echo=FALSE, results='hold', fig.show='hide'}
### Q9

#Q9 Collapsed t-tests
ed_9on13 <- t.test(infile3$Q9 ~ infile3$Q13)
ed_9on14 <- t.test(infile3$Q9 ~ infile3$Q14c)
ed_9on15 <- t.test(infile3$Q9 ~ infile3$Q15c)
ed_9on16 <- t.test(infile3$Q9 ~ infile3$Q16c)
ed_9on17 <- t.test(infile3$Q9 ~ infile3$Q17c)
ed_9on18 <- t.test(infile3$Q9 ~ infile3$Q18c)
ed_9on19 <- t.test(infile3$Q9 ~ infile3$Q19c)
ed_9on20 <- t.test(infile3$Q9 ~ infile3$Q20c)
ed_9on21 <- t.test(infile3$Q9 ~ infile3$Q21c)
ed_9on22 <- t.test(infile3$Q9 ~ infile3$Q22c)
ed_9on23 <- t.test(infile3$Q9 ~ infile3$Q23c)
ed_9on24 <- t.test(infile3$Q9 ~ infile3$Q24c)
ed_9on25 <- t.test(infile3$Q9 ~ infile3$Q25c)

ed_9on13_adj <- ed_9on13$p.value < Pcritical
ed_9on14_adj <- ed_9on14$p.value < Pcritical
ed_9on15_adj <- ed_9on15$p.value < Pcritical
ed_9on16_adj <- ed_9on16$p.value < Pcritical
ed_9on17_adj <- ed_9on17$p.value < Pcritical
ed_9on18_adj <- ed_9on18$p.value < Pcritical
ed_9on19_adj <- ed_9on19$p.value < Pcritical
ed_9on20_adj <- ed_9on20$p.value < Pcritical
ed_9on21_adj <- ed_9on21$p.value < Pcritical
ed_9on22_adj <- ed_9on22$p.value < Pcritical
ed_9on23_adj <- ed_9on23$p.value < Pcritical
ed_9on24_adj <- ed_9on24$p.value < Pcritical
ed_9on25_adj <- ed_9on25$p.value < Pcritical

out9 <- t(data.frame(c(ed_9on13$p.value, ed_9on13_adj),
                   c(ed_9on14$p.value, ed_9on14_adj),
                   c(ed_9on15$p.value, ed_9on15_adj),
                   c(ed_9on16$p.value, ed_9on16_adj),
                   c(ed_9on17$p.value, ed_9on17_adj),
                   c(ed_9on18$p.value, ed_9on18_adj),
                   c(ed_9on19$p.value, ed_9on19_adj),
                   c(ed_9on20$p.value, ed_9on20_adj),
                   c(ed_9on21$p.value, ed_9on21_adj),
                   c(ed_9on22$p.value, ed_9on22_adj),
                   c(ed_9on23$p.value, ed_9on23_adj),
                   c(ed_9on24$p.value, ed_9on24_adj),
                   c(ed_9on25$p.value, ed_9on25_adj)
                   )
                )

colnames(out9) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out9) <- c("Question 13","Question 14","Question 15","Question 16","Question 17","Question 18","Question 19","Question 20","Question 21","Question 22","Question 23","Question 24","Question 25")

kable(out9,digits=6)
```

There were no significant associations using collapsed T-tests for question nine. 

##### T-Tests for association with Education question 11
```{r Q11 on Education, echo=FALSE, results='hold', fig.show='hide'}
### Q11

#Q11 Collapsed t-tests
ed_11on13 <- t.test(infile3$Q11 ~ infile3$Q13)
ed_11on14 <- t.test(infile3$Q11 ~ infile3$Q14c)
ed_11on15 <- t.test(infile3$Q11 ~ infile3$Q15c)
ed_11on16 <- t.test(infile3$Q11 ~ infile3$Q16c)
ed_11on17 <- t.test(infile3$Q11 ~ infile3$Q17c)
ed_11on18 <- t.test(infile3$Q11 ~ infile3$Q18c)
ed_11on19 <- t.test(infile3$Q11 ~ infile3$Q19c)
ed_11on20 <- t.test(infile3$Q11 ~ infile3$Q20c)
ed_11on21 <- t.test(infile3$Q11 ~ infile3$Q21c)
ed_11on22 <- t.test(infile3$Q11 ~ infile3$Q22c)
ed_11on23 <- t.test(infile3$Q11 ~ infile3$Q23c)
ed_11on24 <- t.test(infile3$Q11 ~ infile3$Q24c)
ed_11on25 <- t.test(infile3$Q11 ~ infile3$Q25c)

ed_11on13_adj <- ed_11on13$p.value < Pcritical
ed_11on14_adj <- ed_11on14$p.value < Pcritical
ed_11on15_adj <- ed_11on15$p.value < Pcritical
ed_11on16_adj <- ed_11on16$p.value < Pcritical
ed_11on17_adj <- ed_11on17$p.value < Pcritical
ed_11on18_adj <- ed_11on18$p.value < Pcritical
ed_11on19_adj <- ed_11on19$p.value < Pcritical
ed_11on20_adj <- ed_11on20$p.value < Pcritical
ed_11on21_adj <- ed_11on21$p.value < Pcritical
ed_11on22_adj <- ed_11on22$p.value < Pcritical
ed_11on23_adj <- ed_11on23$p.value < Pcritical
ed_11on24_adj <- ed_11on24$p.value < Pcritical
ed_11on25_adj <- ed_11on25$p.value < Pcritical

out11 <- t(data.frame(c(ed_11on13$p.value, ed_11on13_adj),
                   c(ed_11on14$p.value, ed_11on14_adj),
                   c(ed_11on15$p.value, ed_11on15_adj),
                   c(ed_11on16$p.value, ed_11on16_adj),
                   c(ed_11on17$p.value, ed_11on17_adj),
                   c(ed_11on18$p.value, ed_11on18_adj),
                   c(ed_11on19$p.value, ed_11on19_adj),
                   c(ed_11on20$p.value, ed_11on20_adj),
                   c(ed_11on21$p.value, ed_11on21_adj),
                   c(ed_11on22$p.value, ed_11on22_adj),
                   c(ed_11on23$p.value, ed_11on23_adj),
                   c(ed_11on24$p.value, ed_11on24_adj),
                   c(ed_11on25$p.value, ed_11on25_adj)
                   )
                )

colnames(out11) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out11) <- c("Question 13","Question 14","Question 15","Question 16","Question 17","Question 18","Question 19","Question 20","Question 21","Question 22","Question 23","Question 24","Question 25")

kable(out11,digits=6)
```

* Those who answered question number 15 as either strongly disagree, disagree, or uncertain had a significantly lower agreement with the statement "My professors have encouraged the use of personalized medicine" than those who answered the question as agree or strongly agree.
* Those who answered question number 19 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My professors have encouraged the use of personalized medicine" than those who answered the question as comfortable or very comfortable.
* Those who answered question number 25 as either not at all comfortable, not very comfortable, or neither comfortable nor uncomfortable had a significantly lower agreement with the statement "My professors have encouraged the use of personalized medicine" than those who answered the question as comfortable or very comfortable.

## Covariate Analysis 
### Further EBPAS Analyses (against covariates using ANOVA, Questions 26-31.2)

Because EBPAS score is a continuous vector of integers and is approximately normally distributed, the appropriate test to use here is ANOVA. We are looking now for associations between EBPAS and the covariates.

##### Covariate Grouping
We need to create a new grouping from Question 28.2 (Year of medical school). We are just merging the M3 and M4 students into one "clinical" grouping, while coding M1s as "pre-didactic" and M2s as "pre-clinical" as was done in Caroline's Poster. The new vector we create is called Q28.2c ("c" for collapsed).

```{r Covariate Grouping}
infile3$Q28.2c <- infile3$Q28.2
infile3$Q28.2c[infile3$Q28.2c==4] <- 3
clinical_grouping_table <- table(infile3$Q28.2c) 
```

In the study, there are `r clinical_grouping_table[[1]]` pre-didactic students, `r clinical_grouping_table[[2]]` pre-clinical students, and `r clinical_grouping_table[[3]]` clinical students.

#### EBPAS ANOVAs

```{r EBPAS ANOVAs on q26, echo=FALSE, fig.show='hide'}

# EBPAS ~ Q26
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q26)))
boxplot(EBPAS ~ Q26, data=infile3)
```
EBPAS not significantly associated wtih question 26 on ANOVA.

```{r EBPAS ANOVAs on q27, echo=FALSE}
# EBPAS ~ Q27
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q27)))
```
EBPAS not significantly associated with question 27 on ANOVA.

```{r EBPAS ANOVAs on q28.2c,echo=FALSE}
# EBPAS ~ Q28.2c (clinical grouping)
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q28.2c)))
#boxplot(EBPAS ~ Q28.2c, data=infile3)
```
EBPAS not significantly associated wtih question 28.2c on ANOVA.

```{r EBPAS ANOVAs on q29.1,echo=FALSE}
# EBPAS ~ Q29.1 ("Are you in a dual degre program?")
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q29.1)))
#boxplot(EBPAS ~ Q29.1, data=infile3)
```
EBPAS not significantly associated wtih question 29.1 on ANOVA.

```{r EBPAS ANOVAs on q29.2,echo=FALSE}
# EBPAS ~ Q29.2 ("If yes, which dual degree program")
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q29.2)))
#boxplot(EBPAS ~ Q29.2, data=infile3)
```
EBPAS not significantly associated wtih question 29.2 on ANOVA.

```{r EBPAS ANOVAs on q30.1,echo=FALSE}
# EBPAS ~ Q30.1
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q30.1)))
#boxplot(EBPAS ~ Q30.1, data=infile3)
```
EBPAS not significantly associated wtih question 30.1 on ANOVA.

```{r EBPAS ANOVAs on q230.2,echo=FALSE}
# EBPAS ~ Q30.2
summary(aov(infile3$EBPAS ~ as.factor(infile3$Q30.2)))
#boxplot(EBPAS ~ Q30.2, data=infile3)
```
EBPAS not significantly associated wtih question 30.2 on ANOVA.

### Education Question Covariate Analysis

I elected to use the Kruskal-Wallis test on the Likert Data instead of ANOVA. Chi-Square assumptions are usually not met without further grouping. KW test is a non-parametric version of one-way ANOVA appropriate here because of ordinal data. The results are summarized in the table below. Correction was done for multiple testing.

##### Question 3 
See table below, output omitted for brevity
```{r Education (No. 3) on Covariates, echo=FALSE, results='hide',fig.show='hide'}

# Q3 ~ Q26
summary(aov(infile3$Q3 ~ as.factor(infile3$Q26)))
kwq3on26 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q26))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q26)))

# Q3 ~ Q27
summary(aov(infile3$Q3 ~ as.factor(infile3$Q27)))
kwq3on27 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q27))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q27)))

# Q3 ~ Q28.2 ("Year of Medical School")
# summary(aov(infile3$Q3 ~ as.factor(infile3$Q28.2)))
# kwq3on28.2 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q28.2))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q28.2)))

# Q3 ~ Q28.2c (clinical grouping)
summary(aov(infile3$Q3 ~ as.factor(infile3$Q28.2c)))
kwq3on28.2 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q28.2c))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q28.2)))

# Q3 ~ Q29.1 ("Are you in a dual degre program?")
summary(aov(infile3$Q3 ~ as.factor(infile3$Q29.1)))
kwq3on29.1 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q29.1))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q29.1)))

# Q3 ~ Q29.2 ("If yes, which dual degree program")
summary(aov(infile3$Q3 ~ as.factor(infile3$Q29.2)))
kwq3on29.2 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q29.2))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q29.2)))

# Q3 ~ Q30.1
summary(aov(infile3$Q3 ~ as.factor(infile3$Q30.1)))
kwq3on30.1 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q30.1))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q30.1)))

# Q3 ~ Q30.2
summary(aov(infile3$Q3 ~ as.factor(infile3$Q30.2)))
kwq3on30.2 <- kruskal.test(infile3$Q3 ~ as.factor(infile3$Q30.2))
#TukeyHSD(aov(infile3$Q3 ~ as.factor(infile3$Q30.2)))
```

##### Question 6
See table below, output omitted for brevity
```{r Education (No. 6) on Covariates, echo=FALSE, results='hide',fig.show='hide'}

# Q6 ~ Q26
summary(aov(infile3$Q6 ~ as.factor(infile3$Q26)))
kwq6on26 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q26))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q26)))

# Q6 ~ Q27
summary(aov(infile3$Q6 ~ as.factor(infile3$Q27)))
kwq6on27 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q27))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q27)))

# Q6 ~ Q28.2 ("Year of Medical School")
# summary(aov(infile3$Q6 ~ as.factor(infile3$Q28.2)))
# kwq6on28.2 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q28.2))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q28.2)))

# Q6 ~ Q28.2c (clinical grouping)
summary(aov(infile3$Q6 ~ as.factor(infile3$Q28.2c)))
kwq6on28.2 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q28.2c))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q28.2)))

# Q6 ~ Q29.1 ("Are you in a dual degre program?")
summary(aov(infile3$Q6 ~ as.factor(infile3$Q29.1)))
kwq6on29.1 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q29.1))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q29.1)))

# Q6 ~ Q29.2 ("If yes, which dual degree program")
summary(aov(infile3$Q6 ~ as.factor(infile3$Q29.2)))
kwq6on29.2 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q29.2))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q29.2)))

# Q6 ~ Q30.1
summary(aov(infile3$Q6 ~ as.factor(infile3$Q30.1)))
kwq6on30.1 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q30.1))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q30.1)))

# Q6 ~ Q30.2
summary(aov(infile3$Q6 ~ as.factor(infile3$Q30.2)))
kwq6on30.2 <- kruskal.test(infile3$Q6 ~ as.factor(infile3$Q30.2))
#TukeyHSD(aov(infile3$Q6 ~ as.factor(infile3$Q30.2)))
boxplot(EBPAS ~ Q6, data=infile3)
```

##### Question 9
See table below, output omitted for brevity
```{r Education (No. 9) on Covariates, echo=FALSE, results='hide',fig.show='hide'}

# Q9 ~ Q26
summary(aov(infile3$Q9 ~ as.factor(infile3$Q26)))
kwq9on26 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q26))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q26)))

# Q9 ~ Q27
summary(aov(infile3$Q9 ~ as.factor(infile3$Q27)))
kwq9on27 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q27))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q27)))

# Q9 ~ Q28.2 ("Year of Medical School")
# summary(aov(infile3$Q9 ~ as.factor(infile3$Q28.2)))
# kwq9on28.2 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q28.2))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q28.2)))

# Q9 ~ Q28.2c (clinical grouping)
summary(aov(infile3$Q9 ~ as.factor(infile3$Q28.2c)))
kwq9on28.2 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q28.2c))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q28.2)))

# Q9 ~ Q29.1 ("Are you in a dual degre program?")
summary(aov(infile3$Q9 ~ as.factor(infile3$Q29.1)))
kwq9on29.1 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q29.1))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q29.1)))

# Q9 ~ Q29.2 ("If yes, which dual degree program")
summary(aov(infile3$Q9 ~ as.factor(infile3$Q29.2)))
kwq9on29.2 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q29.2))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q29.2)))

# Q9 ~ Q30.1
summary(aov(infile3$Q9 ~ as.factor(infile3$Q30.1)))
kwq9on30.1 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q30.1))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q30.1)))

# Q9 ~ Q30.2
summary(aov(infile3$Q9 ~ as.factor(infile3$Q30.2)))
kwq9on30.2 <- kruskal.test(infile3$Q9 ~ as.factor(infile3$Q30.2))
#TukeyHSD(aov(infile3$Q9 ~ as.factor(infile3$Q30.2)))
```

##### Question 11
See table below, output omitted for brevity
```{r Education (No. 11) on Covariates, echo=FALSE, results='hide',fig.show='hide'}

# Q11 ~ Q26 (Age Range)
summary(aov(infile3$Q11 ~ as.factor(infile3$Q26)))
kwq11on26 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q26))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q26)))

# Q11 ~ Q27 (Gender)
summary(aov(infile3$Q11 ~ as.factor(infile3$Q27)))
kwq11on27 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q27))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q27)))

# Q11 ~ Q28.2 ("Year of Medical School")
# summary(aov(infile3$Q11 ~ as.factor(infile3$Q28.2)))
# kwq11on28.2 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q28.2))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q28.2)))

# Q11 ~ Q28.2c (clinical grouping)
summary(aov(infile3$Q11 ~ as.factor(infile3$Q28.2c)))
kwq11on28.2 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q28.2c))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q28.2)))

# Q11 ~ Q29.1 ("Are you in a dual degre program?")
summary(aov(infile3$Q11 ~ as.factor(infile3$Q29.1)))
kwq11on29.1 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q29.1))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q29.1)))

# Q11 ~ Q29.2 ("If yes, which dual degree program")
summary(aov(infile3$Q11 ~ as.factor(infile3$Q29.2)))
kwq11on29.2 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q29.2))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q29.2)))

# Q11 ~ Q30.1
summary(aov(infile3$Q11 ~ as.factor(infile3$Q30.1)))
kwq11on30.1 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q30.1))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q30.1)))

# Q11 ~ Q30.2
summary(aov(infile3$Q11 ~ as.factor(infile3$Q30.2)))
kwq11on30.2 <- kruskal.test(infile3$Q11 ~ as.factor(infile3$Q30.2))
#TukeyHSD(aov(infile3$Q11 ~ as.factor(infile3$Q30.2)))
```

####  Summary Table of Education Question KW Results
```{r KW-Table on Covariates, echo=FALSE}

PCriticalKW <- 0.05/7

print(c("Critical P-Value:  ", PCriticalKW) )

### Question 3
ed_3on26 <- kwq3on26$p.value 
ed_3on27 <- kwq3on27$p.value 
ed_3on28.2 <- kwq3on28.2$p.value 
ed_3on29.1 <- kwq3on29.1$p.value 
ed_3on29.2 <- kwq3on29.2$p.value 
ed_3on30.1 <- kwq3on30.1$p.value 
ed_3on30.2 <- kwq3on30.2$p.value 

ed_3on26_adj <- kwq3on26$p.value < PCriticalKW
ed_3on27_adj <- kwq3on27$p.value < PCriticalKW
ed_3on28.2_adj <- kwq3on28.2$p.value < PCriticalKW
ed_3on29.1_adj <- kwq3on29.1$p.value < PCriticalKW
ed_3on29.2_adj <- kwq3on29.2$p.value < PCriticalKW
ed_3on30.1_adj <- kwq3on30.1$p.value < PCriticalKW
ed_3on30.2_adj <- kwq3on30.2$p.value < PCriticalKW

out3covar <- t(
                  data.frame(
                   c(ed_3on26, ed_3on26_adj),
                   c(ed_3on27, ed_3on27_adj),
                   c(ed_3on28.2, ed_3on28.2_adj),
                   c(ed_3on29.1, ed_3on29.1_adj),
                   c(ed_3on29.2, ed_3on29.2_adj),
                   c(ed_3on30.1, ed_3on30.1_adj),
                   c(ed_3on30.2, ed_3on30.2_adj)
                   )
                )

colnames(out3covar) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out3covar) <- c("Question 26","Question 27","Question 28.2c","Question 29.1","Question 29.2","Question 30.1","Question 30.2")

kable(out3covar,caption="Question 3 Covariate Analysis by KW Test")

### Question 6
ed_6on26 <- kwq6on26$p.value 
ed_6on27 <- kwq6on27$p.value 
ed_6on28.2 <- kwq6on28.2$p.value 
ed_6on29.1 <- kwq6on29.1$p.value 
ed_6on29.2 <- kwq6on29.2$p.value 
ed_6on30.1 <- kwq6on30.1$p.value 
ed_6on30.2 <- kwq6on30.2$p.value 

ed_6on26_adj <- kwq6on26$p.value < PCriticalKW
ed_6on27_adj <- kwq6on27$p.value < PCriticalKW
ed_6on28.2_adj <- kwq6on28.2$p.value < PCriticalKW
ed_6on29.1_adj <- kwq6on29.1$p.value < PCriticalKW
ed_6on29.2_adj <- kwq6on29.2$p.value < PCriticalKW
ed_6on30.1_adj <- kwq6on30.1$p.value < PCriticalKW
ed_6on30.2_adj <- kwq6on30.2$p.value < PCriticalKW

out6covar <- t(
                  data.frame(
                   c(ed_6on26, ed_6on26_adj),
                   c(ed_6on27, ed_6on27_adj),
                   c(ed_6on28.2, ed_6on28.2_adj),
                   c(ed_6on29.1, ed_6on29.1_adj),
                   c(ed_6on29.2, ed_6on29.2_adj),
                   c(ed_6on30.1, ed_6on30.1_adj),
                   c(ed_6on30.2, ed_6on30.2_adj)
                   )
                )

colnames(out6covar) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out6covar) <- c("Question 26","Question 27","Question 28.2c","Question 29.1","Question 29.2","Question 30.1","Question 30.2")

kable(out6covar,caption="Question 6 Covariate Analysis by KW Test")

### Question 9
ed_9on26 <- kwq9on26$p.value 
ed_9on27 <- kwq9on27$p.value 
ed_9on28.2 <- kwq9on28.2$p.value 
ed_9on29.1 <- kwq9on29.1$p.value 
ed_9on29.2 <- kwq9on29.2$p.value 
ed_9on30.1 <- kwq9on30.1$p.value 
ed_9on30.2 <- kwq9on30.2$p.value 

ed_9on26_adj <- kwq9on26$p.value < PCriticalKW
ed_9on27_adj <- kwq9on27$p.value < PCriticalKW
ed_9on28.2_adj <- kwq9on28.2$p.value < PCriticalKW
ed_9on29.1_adj <- kwq9on29.1$p.value < PCriticalKW
ed_9on29.2_adj <- kwq9on29.2$p.value < PCriticalKW
ed_9on30.1_adj <- kwq9on30.1$p.value < PCriticalKW
ed_9on30.2_adj <- kwq9on30.2$p.value < PCriticalKW

out9covar <- t(
                  data.frame(
                   c(ed_9on26, ed_9on26_adj),
                   c(ed_9on27, ed_9on27_adj),
                   c(ed_9on28.2, ed_9on28.2_adj),
                   c(ed_9on29.1, ed_9on29.1_adj),
                   c(ed_9on29.2, ed_9on29.2_adj),
                   c(ed_9on30.1, ed_9on30.1_adj),
                   c(ed_9on30.2, ed_9on30.2_adj)
                   )
                )

colnames(out9covar) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out9covar) <- c("Question 26","Question 27","Question 28.2c","Question 29.1","Question 29.2","Question 30.1","Question 30.2")

kable(out9covar,caption="Question 9 Covariate Analysis by KW Test")

### Question 11
ed_11on26 <- kwq11on26$p.value 
ed_11on27 <- kwq11on27$p.value 
ed_11on28.2 <- kwq11on28.2$p.value 
ed_11on29.1 <- kwq11on29.1$p.value 
ed_11on29.2 <- kwq11on29.2$p.value 
ed_11on30.1 <- kwq11on30.1$p.value 
ed_11on30.2 <- kwq11on30.2$p.value 

ed_11on26_adj <- kwq11on26$p.value < PCriticalKW
ed_11on27_adj <- kwq11on27$p.value < PCriticalKW
ed_11on28.2_adj <- kwq11on28.2$p.value < PCriticalKW
ed_11on29.1_adj <- kwq11on29.1$p.value < PCriticalKW
ed_11on29.2_adj <- kwq11on29.2$p.value < PCriticalKW
ed_11on30.1_adj <- kwq11on30.1$p.value < PCriticalKW
ed_11on30.2_adj <- kwq11on30.2$p.value < PCriticalKW

out11covar <- t(data.frame(c(ed_11on26, ed_11on26_adj),
                   c(ed_11on27, ed_11on27_adj),
                   c(ed_11on28.2, ed_11on28.2_adj),
                   c(ed_11on29.1, ed_11on29.1_adj),
                   c(ed_11on29.2, ed_11on29.2_adj),
                   c(ed_11on30.1, ed_11on30.1_adj),
                   c(ed_11on30.2, ed_11on30.2_adj)
                   )
                )

colnames(out11covar) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(out11covar) <- c("Question 26","Question 27","Question 28.2c","Question 29.1","Question 29.2","Question 30.1","Question 30.2")

kable(out11covar,caption="Question 11 Covariate Analysis by KW Test")
```

* Question 3 is signficiant for an association with clinical grouping  (28.2c)
* Question 6 is signficiant for an association with clinical grouping  (28.2c)
* Question 9 is signficiant for an association with interest in a research career  (30.1)
* Question 11 is signficiant for an association with clinical grouping  (28.2c)

More detail on these significant results in the next section.

####  Post-Hoc Tests on Significant KW Tests

We use the Dunn test to test for pairwise differences following KW significance tests. This is a non-parametric equivalent to the Tukey test folowing ANOVA. The multiple-comparisons correction here is for family-wise error rate (FWER) using the Benjamini-Hochberg method as implemented in the dunn.test R package.
 
##### Question Three:
```{r Post-Hoc Dunn Tests for significant KW Tests Q3, echo=FALSE}
dunn.test(x=infile3$Q3, g=as.factor(infile3$Q28.2c), method="bh", alpha=0.05,wrap=FALSE)
ddply(infile3, ~Q28.2c, summarize, mean=mean(Q3, na.rm=TRUE), median=median(Q3), N=length(Q6))
```

For question three's significant association with clinical year, we find that group 1 (pre-didactic) is significantly different from group 2 and 3 (pre-clinical and clinical). The pre-clinical and clinical groups are not significantly different from each other.

Pre-didactic students are significantly less likely to agree with the statement "My medical education has adequately prepared me to practice personalized medication" than are either pre-clinical or clinical students.

##### Question Six:
```{r Post-Hoc Dunn Tests for significant KW Tests Q6, echo=FALSE}
dunn.test(x=infile3$Q6, g=as.factor(infile3$Q28.2c), method="bh", alpha=0.05,wrap=FALSE)
ddply(infile3, ~Q28.2c, summarize, mean=mean(Q6, na.rm=TRUE), median=median(Q6), N=length(Q6))
```

For question six's significant association with clinical year, we find that group 1 (pre-didactic) is significantly different from group 2 and 3 (pre-clinical and clinical). The pre-clinical and clinical groups are not significantly different from each other.

Pre-clinical students are significantly less likely to agree with the statement "I know whom to ask questions regarding genomic testing" than are either pre-clinical or clinical students. The pre-clinical and clinical groups were not significantly different from each other.

##### Question Nine:
```{r Post-Hoc Dunn Tests for significant KW Tests Q9, echo=FALSE}
dunn.test(x=infile3$Q9, g=as.factor(infile3$Q30.1), method="bh", alpha=0.05,wrap=FALSE)
ddply(infile3, ~Q30.1, summarize, mean=mean(Q9, na.rm=TRUE), median=median(Q9), N=length(Q9))
```

For educational question nine, those who do not want to have a research career ("0") are significantly different from those who do want a research career, but not significantly different from those who are not sure if they want a research career. Those who do want a research career are significantly different from those who do not want a research career and those who are not sure if they want a research career.

Students who want a research career are significantly more likely to agree with the statement "I think it is important to learn about personalized medicine" than both students who are not sure if they want a research career and students who do not want a research career. Students who do not want a research career are not significantly different in their agreement with this statement than those who do not know if they want a research career.


```{r Post-Hoc Dunn Tests for significant KW Tests Q11, echo=FALSE}
dunn.test(x=infile3$Q11, g=as.factor(infile3$Q28.2c), method="bh", alpha=0.05,wrap=FALSE)
ddply(infile3, ~Q28.2c, summarize, mean=mean(Q11, na.rm=TRUE), median=median(Q11), N=length(Q11))
```

Pre-didactic students are significantly less likely to agree with the statement "My professors have encouraged the use of personalized medicine" then either pre-clinical or clinical students. Pre-clinical students are significantly MORE LIKELY to agree with the statement than either pre-clinical OR clinical students. Clinical students are signiciantly more likely to agree with the statement than pre-didactic students, but significantly less likely to agree with the statement than pre-clinical students.

## Genomic Testing Question Analysis (Pooled Q18-25)

Because our Cronbach's Alpha was >0.90 for the two genomic testing sections, we can pool the data together and conduct analysis to test for associations with the covariates in questions 26-30.2.

```{r Genomic Testing Question Analysis, echo=FALSE}

infile3 <- mutate(infile3, genomics=Q18+Q19+Q20+Q21+Q22+Q23+Q24+Q25)

par(mfrow=c(1,2))
barplot(sort(infile3$genomics),xlab='Respondent',main="Sorted Totals for Genomics Total Score")
hist(infile3$genomics,xlab="Genomics Score",breaks=11,main="Histogram of Genomics Total Score")

gen_26 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q26)))
gen_27 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q27)))
gen_28.2 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q28.2c)))
gen_29.1 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q29.1)))
gen_29.2 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q29.2)))
gen_30.1 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q30.1)))
gen_30.2 <- anova(lm(infile3$genomics ~ as.factor(infile3$Q30.2)))

# For this form of ANOVA, to access the P-Value, you unfortunately need to add [[5]][1] to the saved result.

### Question 3
gen_26_p <- gen_26[[5]][1]
gen_27_p <- gen_27[[5]][1]
gen_28.2_p <- gen_28.2[[5]][1]
gen_29.1_p <- gen_29.1[[5]][1]
gen_29.2_p <- gen_29.2[[5]][1]
gen_30.1_p <- gen_30.1[[5]][1]
gen_30.2_p <- gen_30.2[[5]][1]

PCritical_Gen <- 0.05/7

gen_26_p_adj <- gen_26[[5]][1] < PCritical_Gen
gen_27_p_adj <- gen_27[[5]][1] < PCritical_Gen
gen_28.2_p_adj <- gen_28.2[[5]][1] < PCritical_Gen
gen_29.1_p_adj <- gen_29.1[[5]][1] < PCritical_Gen
gen_29.2_p_adj <- gen_29.2[[5]][1] < PCritical_Gen
gen_30.1_p_adj <- gen_30.1[[5]][1] < PCritical_Gen
gen_30.2_p_adj <- gen_30.2[[5]][1] < PCritical_Gen

gen_out_covar <- t(data.frame(
                   c(gen_26_p, gen_26_p_adj),
                   c(gen_27_p, gen_27_p_adj),
                   c(gen_28.2_p, gen_28.2_p_adj),
                   c(gen_29.1_p, gen_29.1_p_adj),
                   c(gen_29.2_p, gen_29.2_p_adj),
                   c(gen_30.1_p, gen_30.1_p_adj),
                   c(gen_30.2_p, gen_30.2_p_adj)
                   )
                )

colnames(gen_out_covar) <- c("P Value", "Significant (1=Yes, 0=No)")
rownames(gen_out_covar) <- c("Question 26","Question 27","Question 28.2","Question 29.1","Question 29.2","Question 30.1","Question 30.2")

kable(gen_out_covar,caption="Genomics Covariate ANOVA Analysis (P-Values)")
```

```{r, echo=FALSE}
ddply(infile3, ~Q27, summarize, mean=mean(genomics, na.rm=TRUE), N=length(genomics))
ddply(infile3, ~Q28.2c, summarize, mean=mean(genomics, na.rm=TRUE), N=length(genomics))
```

```{r Tukey-HSD for genomics, echo=FALSE}
TukeyHSD(aov(infile3$genomics ~ as.factor(infile3$Q27)))
TukeyHSD(aov(infile3$genomics ~ as.factor(infile3$Q28.2c)))
```

* Males were significantly more likely to score a higher result on the genomics section (questions 18-25) than were females. (p<0.0018) __Obviously this is not a real result: We will build a linear model to control for male's apparent tendency to overrate their genetic testing knowledge and ability__.
*  Pre-didactic students scored significantly lower on the genomics section when compared to either clinical (P<0.0000001) or pre-clinical (p<0.0000214) students. Pre-clinical and clinical students did not score significantly differently.

### Regression model for genomics section

We want to build a model using questions 26-30.2 to predict score on the genetics/genomics section of the survey.

```{r regression model, echo=FALSE}
## Research interest (clinical and translational vs. basic)
# Attempt number one: put everything into 3 categories
# Putting clinical and translational together
infile3$Q30c <- infile3$Q30.2
infile3$Q30c[infile3$Q30c==4] <- 0
infile3$Q30c[infile3$Q30c==1] <- 1
infile3$Q30c[infile3$Q30c==2] <- 1
infile3$Q30c[infile3$Q30c==3] <- 2

infile3$Q30c[infile3$Q30c==12] <- 1
infile3$Q30c[infile3$Q30c==23] <- 2
infile3$Q30c[infile3$Q30c==123] <- 0
infile3$Q30c[infile3$Q30c==1234] <- 0

table(infile3$Q30c)
infile3$Q30c <- as.factor(infile3$Q30c)
#levels(infile3$Q30c)

# Attempt number two: put everything into 3 categories
# Putting translational and basic science together
infile3$Q30c <- infile3$Q30.2
infile3$Q30c[infile3$Q30c==4] <- 0
infile3$Q30c[infile3$Q30c==1] <- 1
infile3$Q30c[infile3$Q30c==2] <- 2
infile3$Q30c[infile3$Q30c==3] <- 2

infile3$Q30c[infile3$Q30c==12] <- 1
infile3$Q30c[infile3$Q30c==23] <- 2
infile3$Q30c[infile3$Q30c==123] <- 0
infile3$Q30c[infile3$Q30c==1234] <- 0

table(infile3$Q30c)
infile3$Q30c <- as.factor(infile3$Q30c)
#levels(infile3$Q30c)

## Re-Do Level analysis for Q 30.1
infile3$Q30.1c <- infile3$Q30.1
infile3$Q30.1c[infile3$Q30.1c==2] <- 0
infile3$Q30.1c <- as.factor(infile3$Q30.1c)
table(infile3$Q30.1c)

infile3$Q27.f <- as.factor(infile3$Q27)
infile3$Q29.1.f <- as.factor(infile3$Q29.1) 
infile3$Q30.1.f <- as.factor(infile3$Q30.1) 

model1 <- lm(genomics ~ Q26 + Q27.f + Q28.2 + Q29.1.f + Q30.1.f + Q30c,  data = infile3)
summary(model1)

model2 <- lm(genomics ~ Q27.f + Q28.2 + Q29.1.f + Q30.1.f + Q30c,  data = infile3)
summary(model2)

model3A <- lm(genomics ~ Q27.f + Q28.2 + Q29.1.f + Q30.1.f,  data = infile3)
summary(model3A)

model3B <- lm(genomics ~ Q27.f + Q28.2 + Q29.1.f + Q30c,  data = infile3)
summary(model3B)

model4 <- lm(genomics ~ Q27.f + Q28.2 + Q29.1 + Q30.1.f,  data = infile3)
summary(model4)

model5 <- lm(genomics ~ Q27.f + Q28.2 + Q30c ,data=infile3)
summary(model5)

### Re-doing models with new Q30.1c
model1 <- lm(genomics ~ Q26 + Q27 + Q28.2 + Q29.1.f + Q30.1c + Q30c,  data = infile3)
summary(model1)

model2 <- lm(genomics ~ Q27 + Q28.2 + Q29.1.f + Q30.1c + Q30c,  data = infile3)
summary(model2)

```

